A Horrocks-type theorem for even orthogonal $K_2$

### 2020-06-30 horrocks.tex
Beautify bibliography

Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of the following data:
\begin{enumerate} [label=\normalfont(\arabic*)]
 \item a group $N$ acting on itself by left conjugation (i.\,e. ${}^{n}\!n' = n n' n^{-1}$).
 \item a group $M$ with a left action of $N$ (we call such a group an $N$-group and use the notation ${}^n m$ to denote the image of an element $m\in M$ under the action of $n \in N$);
 \item a homomorphism $\mu \colon M\to N$ preserving the action of $N$-groups and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
\end{enumerate}
It can be shown that the image of $\mu$ is always a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$.

@@

\printbibliography
\Addresses
\begin{filecontents}{horrocks.bib}
@Article{Abe83,
    Title = {Whitehead groups of {C}hevalley groups over polynomial rings},
    Author = {Abe, Eiichi},
    Journal = {Comm. Alg.},
    Year = {1983},
    Number = {12},
    Pages = {1271-1307},
    Volume = {11},
    Doi = {10.1080/00927878308822906} }

@Article{Ka77,
    Title = {Another presentation for {S}teinberg groups},
    Author = {Kallen, Wilberd van der},
    Journal = {Indag. Math.},
    Volume = {80},
    Number = {4},
    Pages = {304--312},
    Year = {1977},
    Doi = {10.1016/1385-7258(77)90026-9} }

@Book{Lam10,
    Title = {Serre's problem on projective modules},
    Author = {Lam, Tsit-Yuen},
    Publisher = {Springer Science \& Business Media},
    Year = {2010},
    Doi = {10.1007/978-3-540-34575-6} }

@Article{LS17,
    Title = {Centrality of odd orthogonal $K_2$},
    Author = {Lavrenov, A. and Sinchuk, S.},
    Journal = {J. Pure Appl. Alg.},
    Volume = {221},
    Year = {2017},
    Pages = {1134--1145},
    url = {https://arxiv.org/pdf/1606.00272.pdf} }

@Inproceedings{RS76,
    Title = {Finitely presented groups of matrices},
    Author = {Rehmann, Ulf and Soul{\'e} , Christophe},
    Booktitle = {Algebraic K-Theory},
    Publisher = {Springer},
    Year = {1976},
    Pages = {164--169},
    Series = {Lect. Notes. Math.},
    Volume = {551},
    Doi = {10.1007/BFb0079999} }

@Article{S15,
    Title = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },
    Author = {Sinchuk, Sergey},
    Journal = {J. Pure Appl. Alg.},
    Year = {2016},
    Number = {2},
    Pages = {857--875},
    Volume = {220},
    Doi = {10.1016/j.jpaa.2015.08.003} }

@Article{St-poly,
    Title = {Homotopy invariance of non-stable $K_1$-functors},
    Author = {Stavrova, Anastasia},
    Journal = {J. K-th.},
    Year = {2014},
    Number = {2},
    Pages = {199--248},
    Volume = {13},
    Doi = {10.1017/is013006012jkt232} }

@Article{St-serr,
    Title = {Non-stable $K_1$-functors of multiloop groups},
    Author = {Stavrova, Anastasia},
    Journal = {Canad. J. Math.},
    Year = {2014},
    Doi = {10.4153/CJM-2015-035-2} }

@Book{St67,
    Title = {Lectures on Chevalley groups},
    Author = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
    Year = {1967},
    Publisher = {Yale Univ. New Haven}}

@Article{Ste73,
    Title = {Surjective stability in dimension 0 for $K_2$ and related functors},
    Author = {Stein, Michael R.},
    Journal = {Trans. Amer. Math. Soc.},
    Year = {1973},
    Pages = {165--191},
    Volume = {178},
    Doi = {10.2307/1996696} }

@Article{Su77,
    Title = {On the structure of the special linear group over commutative rings},
    Author = {Suslin, Andrei},
    Journal = {Math. USSR Izv.},
    Year = {1977},
    Pages = {221--238},
    Volume = {11},
    Doi = {10.1070/IM1977v011n02ABEH001709} }

@Article{Tu83,
    Title = {The {S}teinberg group of a polynomial ring},
    Author = {Tulenbaev, Marat},
    Journal = {Math. USSR Sb.},
    Year = {1983},
    Pages = {131--144},
    Volume = {45},
    Doi = {10.1070/SM1983v045n01ABEH002591} }

@Article{ST76,
  author    = {Suslin, Andrei and Tulenbaev, Marat},
  title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
  journal   = {J. Soviet Math.},
  year      = {1981},
  volume    = {17},
  number    = {2},
  pages     = {1804-1819},
  doi       = {10.1007/BF01091768}}

@Book{Kbook,
    Title = {The $K$-book: An introduction to algebraic $K$-theory},
    Author = {Weibel, Charles A},
    Volume = {145},
    Year = {2013},
    Publisher = {Amer. Math. Soc.},
    Series = {Grad. Texts Math.} }

@Article{Vav09,
    Title = {Weight elements of Chevalley groups},
    Author = {Vavilov, Nikolai A.},
    Journal = {St. Petersburg Math. J.},
    Year = {2009},
    Number = {1},
    Pages = {23--57},
    Volume = {20},
    Doi = {10.1090/S1061-0022-08-01036-4} }

@Article{We14,
    Title = {On homology of linear groups over $k[t]$},
    Author = {Wendt, Matthias},
    Journal = {Math. Res. Lett.},
    Year = {2014},
    Number = {6},
    Volume = {21},
    Doi = {10.4310/MRL.2014.v21.n6.a15} }

@Article{Ma69,
    title = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},
    author = {Matsumoto, H.},
    journal = {Ann. Sci. ENS},
    year = {1969},
    number = {1},
    pages = {1--62},
    volume = {2},
    url = {http://eudml.org/doc/81843} }

@article{AF17,
    title = {An explicit KO-degree map and applications},
    author = {Asok, Aravind and Fasel, Jean},
    doi = {10.1112/topo.12007},
    volume = 10,
    Issue = 1,
    Year = 2017,
    Pages = {268-300},
    Journal = {J. Top.} }

@article{Sch16,
    author = {Schlichting, Marco},
    title = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
    year = 2017,
    volume = 221,
    Issue = 7,
    Pages = {1729--1844},
    Doi = {10.1016/j.jpaa.2016.12.026},
    Journal = {J. Pure Appl. Alg.} }

@article{FRS12,
    title = {On stably free modules over affine algebras},
    author = {Fasel, Jean and Rao, Ravi and Swan, Richard},
    Volume = 116,
    Issue = 1,
    Pages = {223--243},
    Year = 2012,
    Journal = {Publ. Math. IH{\'E}S},
    doi = {10.1007/s10240-012-0041-y} }

@article{Lo78,
    author = {Loday, Jean-Louis},
    journal = {J. Alg.},
    title = {Cohomologie et groupes de Steinberg relatifs},
    year = {1978},
    volume = {54},
    number = {1},
    doi = {10.1016/0021-8693(78)90025-X},
    pages = {178--202} }

@article{Pa89,
    author = {Panin, Ivan},
    title = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
    journal = {Leningrad Math. J.},
    year = {1990},
    volume = {1},
    number = {3},
    url = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf},
    pages = {741--754} }

@article{Ka80,
    title = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},
    author = {Karoubi, Max},
    journal = {Ann. Math.},
    volume = {112},
    number = {2},
    pages = {259--282},
    year = {1980},
    doi = {10.2307/1971147} }

@article{Hur77,
    author = {Hurrelbrink, J{\"u}rgen},
    title = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
    journal = {Math. Ann.},
    volume = {225},
    year = {1977},
    number = {2},
    pages = {123--129},
    doi = {10.1007/BF01351716} }

@online{Re75,
    title = {\href { http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf } { Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$ }},
    author = {Rehmann, Ulf},
    year = {1975} }

@article{MR91,
    title = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},
    author = {Morita, Jun and Rehmann, Ulf},
    journal = {Math. Z.},
    volume = {206},
    number = {1},
    pages = {57--66},
    year = {1991},
    doi = {10.1007/BF02571324} }

@article{VP,
    year = {1996},
    journal = {Acta Appl. Math.},
    volume = {45},
    issue = {1},
    doi = {10.1007/BF00047884},
    title = {Chevalley groups over commutative rings: I. Elementary calculations},
    author = {Vavilov, Nikolai A. and Plotkin, E.},
    pages = {73--113} }

@article{St71,
    title = {Generators, relations and coverings of Chevalley groups over commutative rings},
    author = {Stein, Michael R},
    journal = {Amer. J. Math.},
    volume = {93},
    number = {4},
    pages = {965--1004},
    year = {1971},
    doi = {10.2307/2373742} }

@inproceedings{DS73,
    title = {The functor $K_2$: A survey of computations and problems},
    author = {Dennis, R Keith and Stein, Michael R},
    booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
    pages = {241--303},
    year = {1973},
    publisher = {Springer},
    doi = {10.1007/BFb0073728} }

@article{Ho05,
    title = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},
    author = {Hornbostel, Jens},
    journal = {J. Top.},
    volume = {44},
    number = {3},
    pages = {661--687},
    year = {2005},
    doi = {10.1016/j.top.2004.10.004} }

@Article{V00,
    title = {A third look at weight diagrams},
    author = {Vavilov, Nikolai A.},
    journal = {Rend. Sem. Mat. Univ. Padova},
    year = {2000},
    pages = {201--250},
    volume = {104},
    Url = {http://eudml.org/doc/108535} }

@article{A13,
    author = {Allcock, Daniel},
    title = {Steinberg groups as amalgams},
    journal = {Alg. Number Th.},
    year = {2016},
    volume = {10},
    number = {8},
    pages = {1791--1843},
    doi = {10.2140/ant.2016.10.1791} }

@article{Su82,
    title = {Quadratic modules and the orthogonal group over polynomial rings},
    author = {Suslin, A.~A. and Kopeiko, V.~I.},
    journal = {J. Soviet Math.},
    volume = {20},
    number = {6},
    pages = {2665--2691},
    year = {1982},
    doi = {10.1007/BF01681481} }

@article{Va86,
    author = {Vaserstein, L.},
    title = {On normal subgroups of Chevalley groups over commutative rings},
    journal = {Tohoku Math. J.},
    volume = {38},
    issue = {2},
    pages = {219--230},
    year = {1986},
    doi = {10.2748/tmj/1178228489} }

@online{VZ18,
    author = {Vavilov, Nikolai A. and Zhang, Zuhong},
    title = {Generation of relative commutator subgroup in Chevalley groups, II},
    archivePrefix = "arXiv",
    eprint = "1811.11263",
    primaryClass = "math.GR",
    year = {2018} }

@article{St-Ded,
    author = {Stavrova, Anastasia},
    title = {Chevalley groups of polynomial rings over Dedekind domains},
    journal = {J. Gr. Th.},
    volume = {23},
    issue = {1},
    doi = {10.1515/jgth-2019-0100},
    year = {2020}}

@article{Das17,
    title = {$\mathbb{P}^1$-gluing for local complete intersections},
    author = {Das, Mrinal Kanti and Tikader, Soumi and Zinna, Md Ali},
    journal = {Math. Z.},
    pages = {1--19},
    year = {2017},
    doi = {10.1007/s00209-019-02299-5} }

@article{Su76,
    title = {Projective modules over polynomial rings are free},
    author = {Suslin, Andrei},
    journal = {Dokl. Akad. nauk SSSR},
    volume = {229},
    pages = {1063--1066},
    year = {1976},
    url = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} }

@article{Qu76,
    author = "Quillen, Daniel",
    title = "Projective modules over polynomial rings",
    journal = "Inv. Math.",
    year = "1976",
    volume = "36",
    number = "1",
    pages = "167--171",
    doi = "10.1007/BF01390008" }

@article{Ho64,
    title = {Projective modules over an extension of a local ring},
    author = {Horrocks, Geoffrey},
    journal = {Proc. London Math. Soc.},
    volume = {3},
    number = {4},
    pages = {714--718},
    year = {1964},
    doi = {10.1112/plms/s3-14.4.714} }

@article{Mo04,
    title = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},
    author = {Morel, Fabien},
    journal = {Comm. Math. Helv.},
    volume = {79},
    number = {4},
    pages = {689--703},
    year = {2004},
    publisher = {Springer},
    doi = {10.1007/s00014-004-0815-z} }

@article{St78,
    title = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},
    author = {Stein, M.~R.},
    journal = {Japan J. Math.},
    volume = {4},
    issue = {1},
    year = {1978},
    pages = {77--108},
    doi = {10.4099/math1924.4.77} }

@mastersthesis{Vo11,
    author = {V{\"o}lkel, Konrad},
    title = {\href { http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf } { Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie }},
    school = {Uni. Freiburg},
    year = {2011},
    type = {Diplomarbeit}}

@article{Ba74,
  title={Clifford algebras and spinor norms over a commutative ring},
  author={Bass, Hyman},
  journal={Amer. J. Math.},
  volume={96},
  number={1},
  pages={156--206},
  year={1974},
  doi={10.2307/2373586}}

@book{Bou81,
  title={Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
  author={Bourbaki, Nicolas},
  year={1981},
  publisher={Masson}}

@InProceedings{Ta86,
  Title                    = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},
  Author                   = {Taddei, Giovanni},
  Booktitle                = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
  Year                     = {1986},
  Pages                    = {693--710},
  Series                   = {Contemp. Math},
  Volume                   = {55},
  Url                      = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}

@article{La18,
  title={A local-global principle for symplectic $K_2$},
  author={Lavrenov, Andrei},
  year={2018},
  journal={Doc. Math.},
  volume={23},
  pages={653--675},
  doi={10.25537/dm.2018v23.653-675}}
\end{filecontents}
\end{document}

>>>>

Recall that a {\it crossed module} is a triple $(M, N, \mu)$ consisting of the following data:
\begin{enumerate} [label=\normalfont(\arabic*)]
 \item a group $N$ acting on itself by left conjugation (i.\,e. ${}^{n}\!n' = n n' n^{-1}$).
 \item a group $M$ with a left action of $N$ (we call such a group an $N$-group and use the notation ${}^n m$ to denote the image of an element $m\in M$ under the action of $n \in N$);
 \item a homomorphism $\mu \colon M\to N$ preserving the action of $N$ and satisfying {\it Peiffer identity} ${}^{\mu(m)}\!m' = m m' m^{-1}$.
\end{enumerate}
It can be shown that the image of $\mu$ is always a normal subgroup of $N$ and that the kernel of $\mu$, which we denote by $L$, is always contained in the center of $M$.

@@

\printbibliography
\Addresses
\begin{filecontents}{horrocks.bib}
@Article{Abe83,
    Author    = {Abe, Eiichi},
    Title     = {Whitehead groups of {C}hevalley groups over polynomial rings},    
    Journal   = {Comm. Alg.},    
    Number    = 12,
    Volume    = 11,
    Pages     = {1271--1307},
    Year      = 1983,    
    Doi       = {10.1080/00927878308822906}}

@Article{A13,
    Author    = {Allcock, Daniel},
    Title     = {Steinberg groups as amalgams},
    Journal   = {Alg. Number Th.},    
    Volume    = 10,
    Number    = 8,
    Pages     = {1791--1843},
    Year      = 2016,
    Doi       = {10.2140/ant.2016.10.1791}}

@Article{AF17,
    Author    = {Asok, Aravind and Fasel, Jean},
    Title     = {An explicit KO-degree map and applications},    
    Journal   = {J. Top.},
    Volume    = 10,
    Issue     = 1,
    Pages     = {268--300},
    Year      = 2017,    
    Doi       = {10.1112/topo.12007}}

@Article{Ba74,
    Author    = {Bass, Hyman},
    Title     = {Clifford algebras and spinor norms over a commutative ring},    
    Journal   = {Amer. J. Math.},
    Volume    = 96,
    Number    = 1,
    Pages     = {156--206},
    Year      = 1974,
    Doi       = {10.2307/2373586}}

@Book{Bou81,
    Author    = {Bourbaki, Nicolas},
    Title     = {Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
    Publisher = {Masson},
    Year      = 1981}

@Inproceedings{DS73,
    Author    = {Dennis, R. Keith and Stein, Michael R.},
    Title     = {The functor $K_2$: A survey of computations and problems},    
    Booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
    Publisher = {Springer},
    Pages     = {241--303},
    Year      = 1973,
    Doi       = {10.1007/BFb0073728}}

@Article{FRS12,
    Author    = {Fasel, Jean and Rao, Ravi and Swan, Richard},
    Title     = {On stably free modules over affine algebras},
    Journal   = {Publ. Math. IH{\'E}S},
    Volume    = 116,
    Issue     = 1,
    Pages     = {223--243},
    Year      = 2012,
    Doi       = {10.1007/s10240-012-0041-y}}

@Article{Ho05,
    Author    = {Hornbostel, Jens},
    Title     = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},    
    Journal   = {J. Top.},
    Volume    = 44,
    Number    = 3,
    Pages     = {661--687},
    Year      = 2005,
    Doi       = {10.1016/j.top.2004.10.004}}

@Article{Ho64,
    Author    = {Horrocks, Geoffrey},
    Title     = {Projective modules over an extension of a local ring},    
    Journal   = {Proc. London Math. Soc.},
    Volume    = 3,
    Number    = 4,
    Pages     = {714--718},
    Year      = 1964,
    Doi       = {10.1112/plms/s3-14.4.714}}

@Article{Hur77,
    Author    = {Hurrelbrink, J{\"u}rgen},
    Title     = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
    Journal   = {Math. Ann.},
    Volume    = 225,    
    Number    = 2,
    Pages     = {123--129},
    Year      = 1977,
    Doi       = {10.1007/BF01351716}}

@Article{Ka80,
    Author    = {Karoubi, Max},
    Title     = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},    
    Journal   = {Ann. Math.},
    Volume    = 112,
    Number    = 2,
    Pages     = {259--282},
    Year      = 1980,
    Doi       = {10.2307/1971147}}

@Book{Lam10,
    Title     = {Serre's problem on projective modules},
    Author    = {Lam, Tsit-Yuen},
    Publisher = {Springer Science \& Business Media},
    Year      = {2010},
    Doi       = {10.1007/978-3-540-34575-6}}

@Article{LS17,
    Author    = {Lavrenov, Andrei and Sinchuk, Sergey},
    Title     = {Centrality of odd orthogonal $K_2$},    
    Journal   = {J. Pure Appl. Alg.},
    Volume    = 221,
    Pages     = {1134--1145},
    Year      = 2017,    
    Url       = {https://arxiv.org/pdf/1606.00272.pdf}}

@Article{La18,
    Author    = {Lavrenov, Andrei},
    Title     = {A local-global principle for symplectic $K_2$},    
    Journal   = {Doc. Math.},    
    Volume    = 23,
    Pages     = {653--675},
    Year      = 2018,
    Doi       = {10.25537/dm.2018v23.653-675}}

@Article{Lo78,
    Author    = {Loday, Jean-Louis},
    Title     = {Cohomologie et groupes de Steinberg relatifs},
    Journal   = {J. Alg.},    
    Volume    = 54,
    Number    = 1,
    Pages     = {178--202},
    Year      = 1978,
    Doi       = {10.1016/0021-8693(78)90025-X}}

@Article{Ma69,
    Author    = {Matsumoto, Hideya},
    Title     = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},    
    Journal   = {Ann. Sci. ENS},
    Volume    = 2,
    Number    = 1,
    Pages     = {1--62},
    Year      = 1969,
    Url       = {http://eudml.org/doc/81843}}

@Article{Mo04,
    Author    = {Morel, Fabien},
    Title     = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},    
    Journal   = {Comm. Math. Helv.},
    Volume    = 79,
    Number    = 4,
    Pages     = {689--703},
    Year      = 2004,
    Doi       = {10.1007/s00014-004-0815-z}}

@Article{MR91,
    Author    = {Morita, Jun and Rehmann, Ulf},
    Title     = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},    
    Journal   = {Math. Z.},
    Volume    = 206,
    Number    = 1,
    Pages     = {57--66},
    Year      = 1991,
    Doi       = {10.1007/BF02571324}}

@Article{Pa89,
    Author    = {Panin, Ivan},
    Title     = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
    Journal   = {Leningrad Math. J.},    
    Volume    = 1,
    Number    = 3,
    Pages     = {741--754},
    Year      = 1990,
    Url       = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf}}

@Article{Qu76,
    Author    = {Quillen, Daniel},
    Title     = {Projective modules over polynomial rings},
    Journal   = {Inv. Math.},    
    Volume    = 36,
    Number    = 1,
    Pages     = {167--171},
    Year      = 1976,
    Doi       = {10.1007/BF01390008}}

@Article{Re75,
    Author    = {Rehmann, Ulf},
    Title     = {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$},    
    Year      = {1975},
    Url       = {http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}}

@Inproceedings{RS76,
    Author    = {Rehmann, Ulf and Soul{\'e} , Christophe},
    Title     = {Finitely presented groups of matrices},    
    Booktitle = {Algebraic K-Theory},
    Publisher = {Springer},        
    Series    = {Lect. Notes. Math.},
    Volume    = 551,
    Pages     = {164--169},
    Year      = 1976,
    Doi       = {10.1007/BFb0079999}}

@Article{Sch16,
    Author    = {Schlichting, Marco},
    Title     = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
    Journal   = {J. Pure Appl. Alg.},    
    Volume    = 221,
    Issue     = 7,
    Pages     = {1729--1844},
    Year      = 2017,
    Doi       = {10.1016/j.jpaa.2016.12.026}}

@Article{S15,
    Author    = {Sinchuk, Sergey},
    Title     = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },    
    Journal   = {J. Pure Appl. Alg.},
    Volume    = 220,    
    Number    = 2,    
    Pages     = {857--875},
    Year      = 2016,
    Doi       = {10.1016/j.jpaa.2015.08.003}}

@Article{St-Ded,
    Author    = {Stavrova, Anastasia},
    Title     = {Chevalley groups of polynomial rings over Dedekind domains},
    Journal   = {J. Gr. Th.},
    Volume    = 23,
    Issue     = 1,
    Pages     = {121--132},
    Year      = 2020,
    Doi       = {10.1515/jgth-2019-0100}}

@Article{St-poly,
    Author    = {Stavrova, Anastasia},
    Title     = {Homotopy invariance of non-stable $K_1$-functors},    
    Journal   = {J. K-th.},
    Volume    = 13,
    Number    = 2,
    Pages     = {199--248},   
    Year      = 2014,
    Doi       = {10.1017/is013006012jkt232}}

@Article{St78,
    Author    = {Stein, Michael R.},
    Title     = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},    
    Journal   = {Japan J. Math.},
    Volume    = 4,
    Issue     = 1,
    Pages     = {77--108},
    Year      = 1978,
    Doi       = {10.4099/math1924.4.77}}

@Article{St71,
    Author    = {Stein, Michael R},
    Title     = {Generators, relations and coverings of Chevalley groups over commutative rings},
    Journal   = {Amer. J. Math.},
    Volume    = 93,
    Number    = 4,
    Pages     = {965--1004},
    Year      = 1971,
    Doi       = {10.2307/2373742}}

@Article{Ste73,
    Author    = {Stein, Michael R.},
    Title     = {Surjective stability in dimension 0 for $K_2$ and related functors},    
    Journal   = {Trans. Amer. Math. Soc.},
    Volume    = 178,
    Pages     = {165--191},
    Year      = 1973,
    Doi       = {10.2307/1996696}}

@Book{St67,
    Author    = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
    Title     = {Lectures on Chevalley groups},        
    Publisher = {Yale Univ. New Haven},
    Year      = 1967}

@Article{Su77,
    Author    = {Suslin, Andrei},
    Title     = {On the structure of the special linear group over commutative rings},    
    Journal   = {Math. USSR Izv.},        
    Volume    = 11,
    Pages     = {221--238},
    Year      = 1977,
    Doi       = {10.1070/IM1977v011n02ABEH001709}}

@Article{Su76,
    Author    = {Suslin, Andrei},
    Title     = {Projective modules over polynomial rings are free},    
    Journal   = {Dokl. Akad. nauk SSSR},
    Volume    = 229,
    Pages     = {1063--1066},
    Year      = 1976,
    Url       = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf}}

@Article{Su82,
    Author    = {Suslin, Andrei and Kopeiko, Vyacheslav},
    Title     = {Quadratic modules and the orthogonal group over polynomial rings},    
    Journal   = {J. Soviet Math.},
    Volume    = 20,
    Number    = 6,
    Pages     = {2665--2691},
    Year      = 1982,
    Doi       = {10.1007/BF01681481}}

@Article{ST76,
    Author    = {Suslin, Andrei and Tulenbaev, Marat},
    Title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
    Journal   = {J. Soviet Math.},    
    Volume    = 17,
    Number    = 2,
    Pages     = {1804--1819},
    Year      = 1981,
    Doi       = {10.1007/BF01091768}}

@InProceedings{Ta86,
    Author    = {Taddei, Giovanni},
    Title     = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},    
    Booktitle = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
    Series    = {Contemp. Math},
    Volume    = 55,
    Pages     = {693--710},       
    Year      = 1986,
    Url       = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}

@Article{Tu83,
    Author    = {Tulenbaev, Marat},
    Title     = {The Steinberg group of a polynomial ring},    
    Journal   = {Math. USSR Sb.},        
    Volume    = 45,
    Pages     = {131--144},
    Year      = 1983,
    Doi       = {10.1070/SM1983v045n01ABEH002591}}

@Article{Va86,
    Author    = {Vaserstein, Leonid},
    Title     = {On normal subgroups of Chevalley groups over commutative rings},
    Journal   = {Tohoku Math. J.},
    Volume    = 38,
    Issue     = 2,
    Pages     = {219--230},
    Year      = 1986,
    Doi       = {10.2748/tmj/1178228489}}

@Article{V00,
    Author    = {Vavilov, Nikolai},
    Title     = {A third look at weight diagrams},    
    Journal   = {Rend. Sem. Mat. Univ. Padova},   
    Volume    = 104,
    Pages     = {201--250},    
    Year      = 2000,
    Url       = {http://eudml.org/doc/108535}}

@Article{VP,
    Author    = {Vavilov, Nikolai and Plotkin, Eugene},
    Title     = {Chevalley groups over commutative rings: I. Elementary calculations},
    Journal   = {Acta Appl. Math.},    
    Volume    = 45,
    Issue     = 1,
    Pages     = {73--113},
    Year      = {1996},       
    Doi       = {10.1007/BF00047884}}

@Article{VZ18,
    Author    = {Vavilov, Nikolai and Zhang, Zuhong},
    Title     = {Generation of relative commutator subgroups in Chevalley groups. II},    
    Journal   = {Proc. Edinburgh Math. Soc.},
    Volume    = 63,
    Number    = 2,
    Pages     = {497--511},
    Year      = 2020,
    Doi       = {10.1017/S0013091519000555}}

@Mastersthesis{Vo11,
    Author    = {V{\"o}lkel, Konrad},
    Title     = {\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}{Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
    School    = {Uni. Freiburg},
    Type      = {Diplomarbeit}
    Year      = 2011}

@Book{Kbook,
    Author    = {Weibel, Charles A},
    Title     = {The $K$-book: An introduction to algebraic $K$-theory},        
    Publisher = {Amer. Math. Soc.},
    Series    = {Grad. Texts Math.},
    Volume    = 145,
    Year      = 2013}
\end{filecontents}
\end{document}
